%-------------------------
% Resume in LaTeX
% Author : Alessia Bellisario
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}
\usepackage{tabularx}
\usepackage{latexsym}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex,hidelinks=true]{hyperref}
\usepackage{fancyhdr}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\topmargin}{-0.35in}
\addtolength{\textwidth}{0.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{
    The \LaTeX{} source for this resumé can be found at \href{https://github.com/alessbell/resume}{github.com/alessbell/resume}
}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\education}[4]{
  \vspace{0pt}\item[]
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\jobLineItem}[2]{
  \vspace{0pt}\item[]
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSmallSubheadingBreather}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\employerTitle}[3]{
  \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
    \href{#1}{\textbf{#2}} & \textbf{#3} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\educationStart}{\begin{itemize}[leftmargin=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Alessia Bellisario}}\\
  \texttt{\href{mailto:alessia@bellisar.io}{alessia@bellisar.io}} · \texttt{\href{https://aless.co}{https://aless.co}} & \href{https://www.linkedin.com/in/alessiabellisario/}{LinkedIn}  ·  \href{https://github.com/alessbell}{GitHub}\\
  Full Stack Web Engineer & New York or Remote\\
\end{tabular*}

%--------PROGRAMMING SKILLS------------
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Specialties}{ESNext JavaScript, TypeScript, React, Node.js, GraphQL, Webpack, Testing Library, Jest, Next.js}
  \resumeSubItem{More Tools and Languages}{Gatsby, Prettier, Preact, MongoDB, DangerJS, Contentful and other headless CMS}
  \vspace{5px}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \employerTitle
    {https://venmo.com}{Venmo (PayPal)}{May 2020 - Present}
  \resumeSubHeadingListStart
    \jobLineItem
      {Senior Front End Engineer (Full-time, New York, NY)}{}
      \resumeItemListStart
        \resumeItem{Next.js and Webviews}{One of two web tech leads responsible for leading a team of six engineers in migrating the consumer-facing web application (venmo.com) to a Next.js application, including webviews used for core flows in the mobile clients with millions of pageviews per month. Led the i18n/l10n and a11y efforts.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \employerTitle
    {https://sesame.mit.edu}{Massachusetts Institute of Technology (MIT) Energy Initiative}{April 2020 - August 2020}
  \resumeSubHeadingListStart
    \jobLineItem
      {Senior Software Engineer (Contract, Remote)}{}
      \resumeItemListStart
        \resumeItem{SESAME Project}{Built a web application used by energy policy analysts to analyze and compare the impacts of proposed energy pathways. Analysts can create, save and edit pathways and compare downstream effects.}
        \resumeItem{COVID-19 Dashboard}{Built a dashboard that charts the impact of COVID-19 on energy consumption in the United States. Built with Gatsby and deployed using Amazon S3, CloudFront and CodeBuild webhooks. Via CodeBuild cron, new CSVs are fetched daily, the data analyzed and dashboard automatically rebuilt.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \employerTitle
    {https://breather.com}{Breather}{January 2015 - April 2020}
  \resumeSubHeadingListStart
    \jobLineItem
        {Senior Front End Engineer (Full-time, New York, NY)}{January 2019 - Present}
    \resumeItemListStart
        \resumeItem{Tools for Office Customers}
        {Led the development of an extensive suite of administrative tools and internal tooling for creating, managing, accessing and invoicing long-term office bookings, generating tens of millions of dollars of revenue across North America and London, UK in its first year.}
        \resumeItem{Led the Team to Adopt Best Practices to Ship Software Faster}
        {Led the Best Practices Guild in the adoption of tools and processes to improve developer collaboration and led the team in designing a Request For Comments (RFC) process. Developed a CI/CD process and rolled it out to the entire 20 person engineering team.}
    \resumeItemListEnd
    \jobLineItem
        {Front End Engineer (Full-time, New York, NY)}{April 2017 - December 2018}
    \resumeItemListStart
        \resumeItem{Progressive Web App for Landlords}
        {Architected and developed \textit{Onsite} as Breather’s first engineer in the U.S. and leader of the Real Estate Innovations pod. \textit{Onsite} is a PWA made with Preact and Flow, features security and financial reporting and integrates with building access systems used in Class A office towers in Manhattan.}
        \resumeItem{React Component Library}
        {Refactored dozens of components while optimizing \textit{Onsite} in order to ship per-component modules. Resulted in a 72\% reduction in bundle size for one web app and 36\% for another.}
      \resumeItemListEnd
    \jobLineItem
		    {Full Stack Engineer (Full-time, Montréal, Canada)}{January 2015 - March 2017}
		\resumeItemListStart
        \resumeItem{Overhaul Access Controls}
        {Built interfaces for managing critical door code information and inviting meeting attendees via email or magic link. Developed a tool for generating transactional email templates.}
        \resumeItem{Modernize Breather.com}
        {Led a progressive rewrite of Breather.com from Backbone to modern React/Redux.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://github.com/alessbell/lines}{Recurse Center}}{Attended the mini 3 batch in April 2019. Built a web app using Rust and WebAssembly that draws happy faces that follow the user's cursor using wasm-bindgen to do direct DOM manipulation from Rust. (2019)}
\resumeSubItem{\href{https://aless.co/gatsby-wasm-plugin/}{gatsby-remark-twitter-cards}}{Built a Gatsby plugin with Rust and WebAssembly that generates Open Graph social card images at build time. It supports vector fonts and handles text layout without native dependencies. (2019)}
% \resumeSubItem{\href{https://github.com/alessbell/wave-tic-tac-toe}{Minimax Tic Tac Toe}}{A tic tac toe game in which a human faces off against an unbeatable computer. Built with Node and Express, the game is played via querystring. (2019)}
\vspace{5px}
\resumeSubHeadingListEnd

%-----------Awards-----------------
% \section{Honors and Awards}
% \begin{description}
% \item[] {\textbf{Above and Beyond} award for exemplifying Breather’s values of contribution and ambition (2017)}
% \vspace{-2px}
% \end{description}

%-----------Presentations----------
\section{Presentations}
\begin{description}
\item[] {\href{https://www.youtube.com/watch?v=6EHbfAmA_0c}{“A QuickStart™ Guide to Making Things on the Internet”} - Google Women Techmakers Montreal (2016)}
\end{description}

%-----------EDUCATION-----------------
\section{Education}
  \educationStart
    \education
      {Bitmaker Labs (Now Bitmaker General Assembly)}{June 2014 - August 2014}
      {JavaScript and Ruby on Rails Bootcamp}{Toronto, Canada}
    \education
      {University of Toronto}{September 2009 - June 2014}
      {Honours Bachelor of Arts in Ethics, Society \& Law}{Toronto, Canada}
    \vspace{-4px}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
